---
title: "supplementary"
format: revealjs
---

## Tajfel's matrices 

```{r}
#| label: matrix-example
#| include: false

matrix <- tibble(
  Response = LETTERS[1:13],
  "...member 8 of the **overestimators** group" = seq(19,7),
  "...member 27 of the **underestimators** group" = seq(1,25, 2)
) |>
  pivot_longer(-Response, 
               names_to = "Person", 
               values_to = "value") |>
  pivot_wider(names_from = Response, 
              values_from = value)
matrix
```

```{r}
#| label: matrix-tab

matrix |> 
  gt() |>
  fmt_markdown(columns = everything()) |> 
  cols_width(
    Person ~ pct(30)  # Make first column narrower
  ) |> 
  tab_options(
    table.width = pct(100),
    table.font.size = px(26),
    column_labels.font.weight = "bold"
  ) |>
  opt_stylize()
```

::: {.incremental .text-small}
- You always assign values to other people (not yourself).
- Select one option (A-M), which corresponds to two values. In this example:
  - M = Maximum joint profit (MJP).
  - A = Ingroup favourtism (for overestimators) (FAV).
  
:::

::: {.citation-footer}
[@bourhis1994]
:::

## Tajfel's matrices 

```{r}
#| label: matrix-tab-repeat

matrix |> 
  gt() |>
  fmt_markdown(columns = everything()) |> 
  cols_width(
    Person ~ pct(30)  # Make first column narrower
  ) |> 
  tab_options(
    table.width = pct(100),
    table.font.size = px(26),
    column_labels.font.weight = "bold"
  ) |>
  opt_stylize()
```

::: {.incremental .text-small}

- This example matrix measures the "pull" of **FAV** on **MJP**.
  - e.g., selecting **A** would count as a "pull" of 12 positions from **M**.
- That value is contrasted to responses on a comparison/control matrix.
- This results in possible values from -12 to +12.
- We will focus on three different types of pull score that index ingroup/outgroup bias.

:::

::: {.citation-footer}
[@bourhis1994]
:::